### 2017-11-01 Draft2/Appending.Growth.tex
Spice up a lemma

\begin{proof}
	I prove that the $\FuncGrow$ algorithm always enforces this using induction. I induct on the number of times $\FuncGrow$ is called, $k$, showing that for all $k \geq 2$, $\FuncGrow$ behaves correctly when called the $k$th time. (At $k = 1$, the growth array is empty, so its behavior is not relevant to this lemma.) I will let $c_i$ and $c_f$ denote the initial and final capacities and $h_i$ and $h_f$ denote the initial and final head capacities for the $k$th call, respectively.

	At $k = 2$, $c_i = \VarInitCapacityNew$. I wish to show that $c_f = \VarGrowthFactorNew\VarInitCapacityNew$. This happens if and only if the next buffer has size $\Delta c = (\VarGrowthFactorNew - 1)\VarInitCapacityNew$, which the algorithm ensures.

	For $k > 2$, by induction $c_i = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew$ and $h_i = (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew$. I wish to show $c_f = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$. Because $k > 2$, the algorithm will calculate $h_f$ as $\VarGrowthFactorNew$ times $h_i$. Then $h_f = \VarGrowthFactorNew h_i = \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$ as desired, and $c_f = c_i + h_f = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$, concluding the proof.
\end{proof}

>>>>

\begin{proof}
	I prove that the $\FuncGrow$ algorithm always enforces this using induction. I induct on the number of times $\FuncGrow$ is called, $k$, showing that for all $k \geq 2$, $\FuncGrow$ behaves correctly when called the $k$th time. (At $k = 1$, the growth array is empty, so its behavior is not relevant to this lemma.) I will let $c_i(k)$ and $c_f(k)$ denote the initial/final capacities and $h_i(k)$ and $h_f(k)$ denote the initial/final head capacities for the $k$th call, respectively.

	For $k = 2$, $c_i(2) = \VarInitCapacityNew$. I wish to show that $c_f(2) = \VarGrowthFactorNew\VarInitCapacityNew$. This happens if and only if the next buffer has size ${\Delta c}(2) = (\VarGrowthFactorNew - 1)\VarInitCapacityNew$, which the algorithm ensures.

	For $k > 2$, by induction $c_i(k) = c_f(k - 1) = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew$ and $h_i(k) = h_f(k - 1) = (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew$. I wish to show $c_f(k) = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f(k) = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$. Because $k > 2$, the algorithm will calculate $h_f$ as $\VarGrowthFactorNew$ times $h_i$. Then
	\begin{align*}
	h_f &= \VarGrowthFactorNew h_i\\
	&= \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew\\
	&= (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew
	\end{align*}
	and
	\begin{align*}
	c_f &= c_i + h_f\\
	&= \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew\\
	&= \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew
	\end{align*}
	as desired.
\end{proof}
